Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-02-28 paper/paper-nature_format.qmd
please work pt 2

![Snapshot of beginning of XML file for Hansard on 25 February 2020](xml1.png){#fig-xml1}

@@

![Portion of XML file for Hansard on 12 December 2002](patternEX.png){#fig-patternEX width="315"}

@@

![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](xml3.png){#fig-xml3 width="345"}

@@

![First 10 rows of lookup table from 19 October 2017 Hansard processing](lookup_ex.png){#fig-lookup width="448"}

@@

![Example of speech with interjections from 21 November 2016 Hansard](interject_ex.png){#fig-interject}

@@

![10 rows of pattern lookup table from 12 December 2012 Hansard processing](pattern_lookup.png){#fig-patterns}

>>>>

![Snapshot of beginning of XML file for Hansard on 25 February 2020](images/xml1.png){#fig-xml1}

@@

![Portion of XML file for Hansard on 12 December 2002](images/patternEX.png){#fig-patternEX width="315"}

@@

![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](images/xml3.png){#fig-xml3 width="345"}

@@

![First 10 rows of lookup table from 19 October 2017 Hansard processing](images/lookup_ex.png){#fig-lookup width="448"}

@@

![Example of speech with interjections from 21 November 2016 Hansard](images/interject_ex.png){#fig-interject}

@@

![10 rows of pattern lookup table from 12 December 2012 Hansard processing](images/pattern_lookup.png){#fig-patterns}

### 2023-02-28 paper/paper-nature_format.tex
please work pt 2

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{January 20, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a key tenet of
democracy, and a critical resource for political science research. In
Australia, following the British tradition, the written record of what
is said in parliament is known as Hansard. While the Australian Hansard
has always been publicly available, it has been difficult to use it for
the purpose of large-scale macro and micro-level text analysis because
it has not been available as a dataset of sufficient quality. Following
the lead of the Linked Parliamentary Data project which achieved this
for Canada, we provide a new, comprehensive, high-quality database that
captures all proceedings of the Australian parliamentary debates from
1998 to the present using Hansard. The database is publicly available
and can be readily linked to other datasets such as election results.
The creation and accessibility of this database will enable the
exploration of questions that are not currently possible to explore,
serving as a valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi

@@

{\centering \includegraphics{xml1.png}

@@

{\centering \includegraphics[width=3.28125in,height=\textheight]{patternEX.png}

@@

{\centering \includegraphics[width=3.59375in,height=\textheight]{xml3.png}

@@

{\centering \includegraphics[width=4.66667in,height=\textheight]{lookup_ex.png}

@@

{\centering \includegraphics{interject_ex.png}

@@

{\centering \includegraphics{pattern_lookup.png}

>>>>

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{February 28, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a key tenet of
democracy, and a critical resource for political science research. In
Australia, following the British tradition, the written record of what
is said in parliament is known as Hansard. While the Australian Hansard
has always been publicly available, it has been difficult to use it for
the purpose of large-scale macro and micro-level text analysis because
it has not been available as a dataset of sufficient quality. Following
the lead of the Linked Parliamentary Data project which achieved this
for Canada, we provide a new, comprehensive, high-quality database that
captures all proceedings of the Australian parliamentary debates from
1998 to the present using Hansard. The database is publicly available
and can be readily linked to other datasets such as election results.
The creation and accessibility of this database will enable the
exploration of questions that are not currently possible to explore,
serving as a valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, enhanced, sharp corners, frame hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

{\centering \includegraphics{images/xml1.png}

@@

{\centering \includegraphics[width=3.28125in,height=\textheight]{images/patternEX.png}

@@

{\centering \includegraphics[width=3.59375in,height=\textheight]{images/xml3.png}

@@

{\centering \includegraphics[width=4.66667in,height=\textheight]{images/lookup_ex.png}

@@

{\centering \includegraphics{images/interject_ex.png}

@@

{\centering \includegraphics{images/pattern_lookup.png}
